Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
represented annotated proofs as files rather than showing them fully in tex

\begin{figure}[!ht]
	$\color{blue}
	\forall \  m. \left\langle \texttt{pn} \mapsto (\texttt{p, n}) \ \ast \ 
	\nodeboxrep(\texttt{n})  \ \ast \ \mathsf{R}(\texttt{n}) \ \big| \ \treerep\ m \
	\right\rangle$
\begin{lstlisting}[language = C, style=myStyle, mathescape=true]
int traverse(pn *pn, int k){
		int flag = 1; 			$\color{blue} \left\{\begin{array}{l}  \mathit{res} = \mathsf{true} \ast  \texttt{pn} \mapsto (\texttt{p, n}) \ast  
				\nodeboxrep(\texttt{n})  \ast \mathsf{R}(\texttt{n})  \ast \treerep\ m 		\end{array}\right\} \Rrightarrow \left\{\begin{array}{l} \mathsf{traverse\_inv} \end{array}\right\}$
		for( ; ; ){ 			$\color{blue} \left\{\begin{array}{l} \mathsf{traverse\_inv} \end{array}\right\} \triangleq \left\{\begin{array}{l} 
			\texttt{pn} \mapsto (\texttt{p, n}) \ast  \nodeboxrep(\texttt{n}) \ast  \mathsf{R}(\texttt{n}) \ast \texttt{k} \in \mathsf{range}(\texttt{n}) \ast \treerep\ m
		 \end{array}\right\}$
				pn->p = pn->n;
				if (pn->p->t == NULL)
						break;
						$\color{violet} \left\{\begin{array}{l} \mathit{res} = \mathsf{true} \ast \texttt{pn} \mapsto (\texttt{n, n}) \ast \texttt{n->t} = \texttt{NULL}  \ast \texttt{n->lock} \lockvar \mathsf{R}(\texttt{n}) \ast \mathsf{R}(\texttt{n}) \ast \texttt{k} \in \mathsf{range}(\texttt{n}) \ast \cdots \end{array}\right\}$
				else{
						int b = findNext(pn, k);
						$\color{blue} \left\{\begin{array}{l} \exists \  \texttt{n'}. \ \texttt{pn} \mapsto (\texttt{n, n}) \ast \texttt{n->t} \neq \texttt{NULL} \ast \\ 
						(\mathit{res'} = \mathsf{false} \ast \texttt{n'} = \texttt{n} \ast  \texttt{n->lock} \lockvar \mathsf{R}(\texttt{n}) \ast \mathsf{R}(\texttt{n}) \ast \cdots )\  \lor \\ 
						(\mathit{res'} = \mathsf{true}  \ast \texttt{pn} \mapsto (\texttt{n, n}) \ast  \texttt{n->lock} \lockvar \mathsf{R}(\texttt{n}) \ast \mathsf{R}(\texttt{n}) \ast \texttt{n->t} \mapsto \texttt{n'} \ast \texttt{n'->lock} \lockvar \mathsf{R}(\texttt{n'}) \ast \cdots)   \end{array}\right\}$
				if (b == 0){
						flag = 0;
						break;
						$\color{violet} \left\{\begin{array}{l} \mathit{res} = \mathsf{false} \ast \texttt{pn} \mapsto (\texttt{n, n}) \ast \texttt{n->t} \neq \texttt{NULL} \ast \texttt{n'} = \texttt{n} \ast \texttt{n->lock} \lockvar \mathsf{R}(\texttt{n}) \ast \mathsf{R}(\texttt{n}) \ast \texttt{k} \in \mathsf{range}(\texttt{n}) \ast \cdots    \end{array}\right\}$
				}
				else{
				$\color{blue} \left\{\begin{array}{l} \mathit{res} = \mathsf{true} \ast \texttt{pn} \mapsto (\texttt{n, n}) \ast  \texttt{n->lock} \lockvar \mathsf{R}(\texttt{n}) \ast \mathsf{R}(\texttt{n}) \ast \texttt{n->t} \mapsto \texttt{n'} \ast \texttt{n'->lock} \lockvar \mathsf{R}(\texttt{n'}) \ast \cdots    \end{array}\right\}$
						acquire(pn->n->lock);
						$\color{blue} \left\{\begin{array}{l} \mathit{res} = \mathsf{true} \ast \texttt{pn} \mapsto (\texttt{n, n}) \ast  \texttt{n->lock} \lockvar \mathsf{R}(\texttt{n}) \ast \mathsf{R}(\texttt{n}) \ast \\ \texttt{n->t} \mapsto \texttt{n'} \ast \texttt{n'->lock} \lockvar \mathsf{R}(\texttt{n'}) \ast \mathsf{R}(\texttt{n'}) \ast \cdots    \end{array}\right\}$
						release(pn->p->lock);
						$\color{blue} \left\{\begin{array}{l} \mathit{res} = \mathsf{true} \ast \texttt{pn} \mapsto (\texttt{n, n}) \ast  \texttt{n->lock} \lockvar \mathsf{R}(\texttt{n}) \ast \\ \texttt{n->t} \mapsto \texttt{n'} \ast \texttt{n'->lock} \lockvar \mathsf{R}(\texttt{n'}) \ast \mathsf{R}(\texttt{n'}) \ast \cdots    \end{array}\right\}$
					}
				}
			}
		return flag;
		$\color{blue} \left\{\begin{array}{l} (\mathit{res} = \mathsf{false} \ast \texttt{pn} \mapsto (\texttt{p', p'}) \ast \texttt{p'->t} \neq \texttt{NULL} \ast \texttt{p'->lock} \lockvar \mathsf{R}(\texttt{p'}) \ast \mathsf{R}(\texttt{p'}) \ast \texttt{k} \in \mathsf{range}(\texttt{p'}) \ast \cdots) \  \lor \\
		(\mathit{res} =\mathsf{true} \ast \texttt{pn} \mapsto (\texttt{p', p'}) \ast \texttt{p'->t} = \texttt{NULL}  \ast \texttt{p'->lock} \lockvar \mathsf{R}(\texttt{p'}) \ast \mathsf{R}(\texttt{p'}) \ast \texttt{k} \in \mathsf{range}(\texttt{p'}) \ast \cdots)
		\end{array}\right\}$
}  \end{lstlisting}
	$\color{blue}
	\left\langle \mathit{res}. \ \exists \  \texttt{n'}.
	\begin{array}{c} \texttt{pn} \mapsto (\texttt{n', n'}) \ \ast 
		\ (\mathit{res} \leftrightarrow (\texttt{n'->t} = \texttt{NULL}))  \ \ast \ \\ \nodeboxrep(\texttt{n'}) \ast \ \mathsf{R}(\texttt{n'})\ \ast \ \texttt{k} \in \mathsf{range}(\texttt{n'})
	\end{array}
	\ \Bigg| \ \treerep\ m \
	\right\rangle$
	\caption{The \texttt{traverse} function in lock-coupling template annotated with separation logic specification}
	\label{proof_lock_traverse}
\end{figure}

@@

\bibliography{../sources}

\appendix

@@

\begin{figure}[!ht]
	\begin{subfigure}{\textwidth}
		$\color{blue}
		\forall m.\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ m
		\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_lock_insert.c}
		$\color{blue}
		\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ (m[\texttt{k} \mapsto \texttt{v}])
		\right\rangle$
		\caption{The \texttt{insert} function in lock-coupling template annotated with separation logic specification. \\\\}
		\label{proof_lock_insert}	
	\end{subfigure}\qquad
	\begin{subfigure}{\textwidth}
		$\color{blue}
		\forall m.\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ m
		\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_insert.c}
		$\color{blue}
		\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ (m[\texttt{k} \mapsto \texttt{v}])
		\right\rangle$
		\caption{The \texttt{insert} function in give-up template annotated with separation logic specification. \\\\}
		\label{proof_giveup_insert}
	\end{subfigure}
	\caption{The \texttt{insert} function in lock-coupling and give-up templates annotated with separation logic specification.}
	\label{proof_lock_giveup_insert}
\end{figure}

>>>>

\begin{figure}[!ht]
	$\color{blue}
	\forall \  m. \left\langle \texttt{pn} \mapsto (\texttt{p, n}) \ \ast \ 
	\nodeboxrep(\texttt{n})  \ \ast \ \mathsf{R}(\texttt{n}) \ \big| \ \treerep\ m \
	\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_lock_traverse.c}
	$\color{blue}
	\left\langle \mathit{res}. \ \exists \  \texttt{n'}.
	\begin{array}{c} \texttt{pn} \mapsto (\texttt{n', n'}) \ \ast 
		\ (\mathit{res} \leftrightarrow (\texttt{n'->t} = \texttt{NULL}))  \ \ast \ \\ \nodeboxrep(\texttt{n'}) \ast \ \mathsf{R}(\texttt{n'})\ \ast \ \texttt{k} \in \mathsf{range}(\texttt{n'})
	\end{array}
	\ \Bigg| \ \treerep\ m \
	\right\rangle$
	\caption{The \texttt{traverse} function in lock-coupling template annotated with separation logic specification}
	\label{proof_lock_traverse}
\end{figure}

@@

\bibliography{../sources}
\newpage
\appendix

@@

\begin{figure}[!ht]
	\begin{subfigure}{\textwidth}
		$\color{blue}
		\forall m.\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ m
		\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_lock_insert.c}
		$\color{blue}
		\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ (m[\texttt{k} \mapsto \texttt{v}])
		\right\rangle$
		\caption{The \texttt{insert} function in lock-coupling template annotated with separation logic specification \\\\}
		\label{proof_lock_insert}	
	\end{subfigure}\qquad
	\begin{subfigure}{\textwidth}
		$\color{blue}
		\forall m.\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ m
		\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_insert.c}
		$\color{blue}
		\left\langle 
		\nodeboxrep\ \texttt{r} \ \big | \ \treerep\ (m[\texttt{k} \mapsto \texttt{v}])
		\right\rangle$
		\caption{The \texttt{insert} function in give-up template annotated with separation logic specification \\\\}
		\label{proof_giveup_insert}
	\end{subfigure}
	\caption{The \texttt{insert} function in lock-coupling and give-up templates annotated with separation logic specification}
	\label{proof_lock_giveup_insert}
\end{figure}
